Title here

### 2016-12-14 portfolio/text/ms.Rmd
Add discussion paragraph

### Summary

- suggests it's mostly an across strategy/permit effect (lowering variability),
  which isn't always a possibility because of regulations and cost
- adjusting within current permit constraints is risky... Not clearly risk
  reducing to generalize from one year to the next, and accounting for effort,
  specializing can increase revenue
- not as simple as increase diversity (within permit) and reduce risk
- methodologically novel: individuals, huge dataset, account for covariates,
  accounting for strategies, keeping annual data (not condensing to mean and
  cv), joint modelling of mean and variance, evaluating within and across
  strategies (different mechanisms of diversification)
- 2 dimensions to think about (revenue and variability); and the trade-off is
  fishery specific: effects within a permit strategy are permit specific;
  sometimes make more money by specializing... some highly variable single
  species permits make a ton of money

@@

- why variability/uncertainty might increase with changes in diversity...
- and how fit in with @kasperski2013, @sethi2012b, @sethi2014
- part of the difference is individuals vs vessels. E.g. @kasperski2013
  suggested that diversity declined following IFQs for halibut sablefish
  vessels. The reason for the decline was that the vessels were allowed to fish
  halibut for more days (because people were sharing boats). At the level of
  people, we wouldn't expect the diversity of someone who only had
  halibut/sablefish permit to be affected by IFQs. The person, not the vessel
  holds the quota share: https://alaskafisheries.noaa.gov/fisheries/ifq
- year to year risky... But maybe evens out/better over time
- diversity within permit - often bycatch, limited room for intentional
  diversification (unless you have a M or salmon permit)
- risk results not really risk, but unpredictability given our covariates ...
  don't change anything and it's most predictable how well you'll do. What's
  unpredictable in our model, might be more predictable on a year to year,
  species by species basis for individual permit holder
- CV vs year-to-year effect for one person

@@

- could vary by time and vary by mean diversity
- spatial/geographic variation
- nonlinear effects
- response to specific events like EVOS

@@

- concerning because in many areas of the world and fisheries, regulations and
  market forces have encouraged specialization / limited (effective)
  diversification (e.g. multiple permits or diverse permits)
- locking into permits limits ability to pick lower risk strategies and is
  getting people locked into low diversity permits that may be doing well now,
  but not necessarily always

@@

>>>>

We fit a hierarchical variance-function regression model to 30 years of
commercial fisheries revenue data in Alaska to simultaneously estimate the
effect of changes in species diversity on individual's revenue and revenue
variability. We find that individuals fishing permit sets that allow high levels
of species diversity tend to have lower revenue variability. Adding an
additional fisheries permit usually increases revenue and decreases revenue
variability. However, within the constraints of a permit and accounting for
effort, specializing (reducing species diversity) tends to increase revenue and
specializing or generalizing tends to be associated with greater revenue
variability, with considerable differences across fisheries. Thus, the most
effective mechanism by which species diversity can lower revenue variability for
individual fishers --- switching or adding fishing permits --- is often costly,
limited by regulations, and unavailable to many individuals.

@@

- why variability/uncertainty might increase with changes in diversity...

- and how fit in with @kasperski2013, @sethi2012b, @sethi2014

- part of the difference is individuals vs vessels. E.g. @kasperski2013
  suggested that diversity declined following IFQs for halibut sablefish
  vessels. The reason for the decline was that the vessels were allowed to fish
  halibut for more days (because people were sharing boats). At the level of
  people, we wouldn't expect the diversity of someone who only had
  halibut/sablefish permit to be affected by IFQs. The person, not the vessel
  holds the quota share: https://alaskafisheries.noaa.gov/fisheries/ifq

- year to year risky... But maybe evens out/better over time

- diversity within permit - often bycatch, limited room for intentional
  diversification (unless you have a M or salmon permit)

- risk results not really risk, but unpredictability given our covariates ...
  don't change anything and it's most predictable how well you'll do. What's
  unpredictable in our model, might be more predictable on a year to year,
  species by species basis for individual permit holder

- CV vs year-to-year effect for one person

@@

There are a number of limitations to our model and extensions that could further
our understanding of the role of diversification...

- could vary by time and vary by mean diversity

- spatial/geographic variation

- nonlinear effects

- response to specific events like EVOS

@@

- concerning because in many areas of the world and fisheries, regulations and
  market forces have encouraged specialization / limited (effective)
  diversification (e.g. multiple permits or diverse permits)

- locking into permits limits ability to pick lower risk strategies and is
  getting people locked into low diversity permits that may be doing well now,
  but not necessarily always

@@

- bring it out to wider than fisheries (farming, timber industry, ...)

- 2 dimensions to think about (revenue and variability); and the trade-off is
  fishery specific: effects within a permit strategy are permit specific;
  sometimes make more money by specializing... some highly variable single
  species permits make a ton of money

- broadly, diversification can provide a powerful form of protection from
  multiple sources of risk to income for those that rely on extracting natural
  resources, but not all forms of diversification are equal, and on an
  individual level there can be economic benefits to specializing and risks to
  adjusting ones strategy

- with increasing environmental variability and extremes due to climate change
  those that rely on natural resources for their livelihoods need approaches to
  buffer risk more than ever

- regulations that limit the ability to diversify can have other considerable
  benefits but it's important to be aware of trade-offs inherent in these
  regulations when making management decisions
